Backward Population Synthesis: Mapping the Evolutionary History of Gravitational-Wave Progenitors

### 2022-10-14 src/tex/ms.tex
Add L165
Deal with 388

We find that the progenitor properties and even the ability to produce a
GW150914-like merger event is strongly correlated with hyperparameter settings;
different assumptions about the black hole masses at merger in GW150914 imply
wildly different formation channels and ZAMS progenitor masses for this event
and some nearby combinations of ZAMS masses are unable, with any reasonable
hyperparameter settings, to produce a DCO merger like GW150914.  We further
exhibit preliminary results of an ongoing analysis over the entire GWTC-3
catalog \citep{GWTC-3} that suggest that the accretion efficiency in stable mass
transfer may depend non-trivially on the primary black hole mass in merging
systems; our methodology allows for a systematic study of such dependencies,
which we will explore more fully in future work.

@@

We show a portion of the joint posterior of the progenitor parameters and
hyperparameters of GW150914 in figure \ref{fig:GW150914_posterior}. Each panel
is colored based on the comparison between progenitor parameters (blue),
hyperparameters (orange), or a mix of the two (green). We find that the choice
for $\sigma$ does not affect the formation of GW150914-like BBHs. This is not
unexpected since we use the \citet{Fryer2012} delayed model which reduces the
natal kick strength at BH formation based on the amount of fallback onto the
proto-CO. In the case of GW150914-like BBHs, the BH progenitors are massive
enough that the fallback reduces the natal kick to zero. Because of this we do
not include $\sigma$ in Figure~\ref{fig:GW150914_posterior}. Similarly, we do
not include the ZAMS orbital period and eccentricity, which are correlated with
one another, but not strongly with the other progenitor parameters or
hyperparameters. We find strong correlations between the ZAMS masses, as well as
strong correlations between $M_{2,\rm{ZAMS}}$ and $f_{\rm{acc}}$, and
$f_{\rm{acc}}$ and $\alpha$. We show scatter plots of each of these combinations
in the upper-right inset of the figure.

>>>>

We find that the progenitor properties and even the ability to produce a
GW150914-like merger event is strongly correlated with hyperparameter settings;
different assumptions about the black hole masses at merger in GW150914 imply
wildly different formation channels and ZAMS progenitor masses for this event
and some nearby combinations of ZAMS masses are unable, with any reasonable
hyperparameter settings, to produce a DCO merger like GW150914.  \textbf{Sensitivity to
hyperparameter choices has been noted before in the context of common envelope
efficiency (CITE Kaze & friends), mass transfer efficiency (cite Monica; Simone
B; etc), and metallicity (cite K.B. & co); <snark>here we can explore all these
choices and more systematically</snark>.}  We further exhibit preliminary results
of an ongoing analysis over the entire GWTC-3 catalog \citep{GWTC-3} that
suggest that the accretion efficiency in stable mass transfer may depend
non-trivially on the primary black hole mass in merging systems; our methodology
allows for a systematic study of such dependencies, which we will explore more
fully in future work.

@@

We show a portion of the joint posterior of the progenitor parameters and
hyperparameters of GW150914 in figure \ref{fig:GW150914_posterior}. Each panel
is colored based on the comparison between progenitor parameters (blue),
hyperparameters (orange), or a mix of the two (green). We find that the choice
for $\sigma$ does not affect the formation of GW150914-like BBHs. This is not
unexpected since we use the \citet{Fryer2012} delayed model which reduces the
natal kick strength at BH formation based on the amount of fallback onto the
proto-CO. In the case of GW150914-like BBHs, the BH progenitors are massive
enough that the fallback reduces the natal kick to zero\textbf{, therefore the inference
result on $\sigma$ is uninformative}. Because of this we do not include $\sigma$
in Figure~\ref{fig:GW150914_posterior}. Similarly, we do not include the ZAMS
orbital period and eccentricity, which are correlated with one another, but not
strongly with the other progenitor parameters or hyperparameters. We find strong
correlations between the ZAMS masses, as well as strong correlations between
$M_{2,\rm{ZAMS}}$ and $f_{\rm{acc}}$, and $f_{\rm{acc}}$ and $\alpha$. We show
scatter plots of each of these combinations in the upper-right inset of the
figure.
